### 2025-04-10 manuscript.Rmd
Update manuscript.Rmd

If the document is reredered and the computational result differs from the original result, the failure to reproduce is noted in the reproducibility report.
In a variation of the previous example, we assume someone changed the value of `x`, the variable `my_sum` would change, and a failure would be displayed (see Figure \@ref(fig:rstudioscreen4)).

>>>>

If the document is rendered again and the computational result differs from the original result, the failure to reproduce is noted in the reproducibility report.
In a variation of the previous example, we assume someone changed the value of `x`, the variable `my_sum` would change, and a failure would be displayed (see Figure \@ref(fig:rstudioscreen4)).
